Data Descriptor: Corresponding author journal publishing activities 2014-2018

### 2019-10-11 analysis/paper.Rmd
minor

---
title: "Data Descriptor: Corresponding author journal publishing activities 2014 - 2018"
output: github_document
author: "Najko Jahn"
bibliography: pubs.bib
csl: chicago.csl
---

>>>>

---
title: "Data Descriptor: Corresponding author journal publishing activities 2014-2018"
output: github_document
bibliography: pubs.bib
csl: chicago.csl
---
